Outputs from time slice analyses

### 2017-12-05 analyses/04-stats.Rmd
added max and min tables

strat <- 
  strat %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

duration <-
  duration %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

number <- 
  number %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

@@

strat2 <- 
  strat2 %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

duration2 <-
  duration2 %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

number2 <- 
  number2 %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

all_peaks <- rbind(strat, duration, number, strat2, duration2, number2)
write.csv(all_peaks, file = paste0("../outputs/peaks.", slug, ".csv"), quote = FALSE, 
          row.names = FALSE)

```
You can rerun for the other datasets by changing the slug name at the start.

>>>>

strat_max <- 
  strat %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

duration_max <-
  duration %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

number_max <- 
  number %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

strat_min <- 
  strat %>%
  group_by(model) %>%
  filter(bs.median == min(bs.median, na.rm = TRUE))

duration_min <-
  duration %>%
  group_by(model) %>%
  filter(bs.median == min(bs.median, na.rm = TRUE))

number_min <- 
  number %>%
  group_by(model) %>%
  filter(bs.median == min(bs.median, na.rm = TRUE))

@@

strat2_max <- 
  strat2 %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

duration2_max <-
  duration2 %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

number2_max <- 
  number2 %>%
  group_by(model) %>%
  filter(bs.median == max(bs.median, na.rm = TRUE))

strat2_min <- 
  strat2 %>%
  group_by(model) %>%
  filter(bs.median == min(bs.median, na.rm = TRUE))

duration2_min <-
  duration2 %>%
  group_by(model) %>%
  filter(bs.median == min(bs.median, na.rm = TRUE))

number2_min <- 
  number2 %>%
  group_by(model) %>%
  filter(bs.median == min(bs.median, na.rm = TRUE))

all_peaks_max <- rbind(strat_max, duration_max, number_max, strat2_max, duration2_max, number2_max)
write.csv(all_peaks_max, file = paste0("../outputs/peaks.max.", slug, ".csv"), quote = FALSE, 
          row.names = FALSE)

all_peaks_min <- rbind(strat_min, duration_min, number_min, strat2_min, duration2_min, number2_min)
write.csv(all_peaks_min, file = paste0("../outputs/peaks.min.", slug, ".csv"), quote = FALSE, 
          row.names = FALSE)
}
```
You can rerun for the other datasets by changing the slug name at the start.
